Drug Toxicity as the Leading Cause of Homeless Deaths in Toronto

### 2024-09-27 paper/paper.qmd
Update paper.qmd

The remainder of this paper is structured as follows: @sec-intro-dataset provides an overview of the raw data set. @ser-variables introduces variables in the cleaned data, and these variables will be used in the visualization. @sec-result presents visualizations of data with explanation of findings from them. Finally, @sec-discussion examines the possible reasons of surge in drug-caused deaths during epidemic, limitations and next steps.

@@

# Discussion

>>>>

The remainder of this paper is structured as follows: @sec-intro-dataset provides an overview of the raw data set. @sec-variables introduces variables in the cleaned data, and these variables will be used in the visualization. @sec-result presents visualizations of data with explanation of findings from them. Finally, @sec-discussion examines the possible reasons of a surge in drug-caused deaths during epidemic, limitations and next steps.

@@

# Discussion{@sec-discussion}
